Counting And Confusion: Bayesian Rate Estimation With Multiple Populations

### 2013-03-06 many.tex
Added TODO re: citation suggested by Hogg for "detecting the undetectable" in a MW stream.

The task of estimating rates of events when a mixture of foreground
and background events is present in data is a common one in physical
and astrophysical applications.  This problem comes up, among others,
in gravitational-wave data analysis
\cite[e.g.,][]{s5-lowmass,s5-highmass,s5-highmass-erratum,s5-lowmass-2,s6-lowmass,s6-highmass}
and in astronomical observations of a field of objects of mixed
provenance \cite{DeGennaro2009}.  In this paper, we introduce a robust
formalism for estimating event rates from the data when the shape of
foreground and background distributions are known (or parameterized),
but the provenance of individual events as either background or
foreground is unknown.

@@

\begin{acknowledgments}
  We thank Kipp Cannon, Chad Hanna, Drew Keppel, Richard
  O'Shaughnessy, and Ted von Hippel for discussions and suggestions
  about this manuscript.  IM and WMF acknowledge the hospitality of
  KITP, supported in part by the National Science Foundation under NSF
  Grant PHY11-25915.  CC's work was carried out at the Jet Propulsion
  Laboratory, California Institute of Technology, under contract to
  the National Aeronautics and Space Administration.  CC also
  gratefully acknowledges support from NSF grant PHY1068881.  JG's
  work is supported by the Royal Society.  Copyright 2013.  All rights
  reserved.
\end{acknowledgments}

>>>>

\will{Find a way to discuss \cite{Koposov2010}.}  The task of
estimating rates of events when a mixture of foreground and background
events is present in data is a common one in physical and
astrophysical applications.  This problem comes up, among others, in
gravitational-wave data analysis
\cite[e.g.,][]{s5-lowmass,s5-highmass,s5-highmass-erratum,s5-lowmass-2,s6-lowmass,s6-highmass}
and in astronomical observations of a field of objects of mixed
provenance \cite{DeGennaro2009}.  In this paper, we introduce a robust
formalism for estimating event rates from the data when the shape of
foreground and background distributions are known (or parameterized),
but the provenance of individual events as either background or
foreground is unknown.

@@

\begin{acknowledgments}
  We thank Kipp Cannon, Thomas Dent, Chad Hanna, Drew Keppel, Richard
  O'Shaughnessy, David Hogg, and Ted von Hippel for discussions and
  suggestions about this manuscript.  IM and WMF acknowledge the
  hospitality of KITP, supported in part by the National Science
  Foundation under NSF Grant PHY11-25915.  CC's work was carried out
  at the Jet Propulsion Laboratory, California Institute of
  Technology, under contract to the National Aeronautics and Space
  Administration.  CC also gratefully acknowledges support from NSF
  grant PHY1068881.  JG's work is supported by the Royal Society.
  Copyright 2013.  All rights reserved.
\end{acknowledgments}
